---
title: "Endocrine Trends in Pandemic"
author: "Kadek Adit Wiryadana"
date: "8 May, 2021 updated in `r format(Sys.time(), '%d %B, %Y')`" 
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(googledrive)
library(bibliometrix)
```

### Akses files in google drives
```{r, eval=FALSE}
drive_auth(
  email = gargle::gargle_oauth_email(),
  path = NULL,
  scopes = "https://www.googleapis.com/auth/drive",
  cache = gargle::gargle_oauth_cache(),
  use_oob = gargle::gargle_oob_default(),
  token = NULL
)
```

### Download data files
```{r, eval=FALSE}
drive_find(n_max = 30) 
drive_download("data.csv")
data <- read.csv("data.csv")
```

### Read data by Bibliometrix
```{r, include=FALSE}
file <- "data.csv"
M <- convert2df(file=file, dbsource = "dimensions", format = "csv")
results <- biblioAnalysis(M, sep = ";")
```

### Summary
```{r}
options(width=100)
S <- summary(object = results, k=10, pause=FALSE)
p <- plot(x = results, k=10, pause=FALSE)
```
### Authors Dominance Ranking
The Dominance Factor is a ratio indicating the fraction of multi-authored articles in which a scholar appears as the first author.

```{r}
DF <- dominance(results, k=10)
DF
```
### H-index of the 10 most productive authors
The h-index is an author-level metric that attempts to measure both the productivity and citation impact of the publications of a scientist or scholar.

The index is based on the set of the scientist’s most cited papers and the number of citations that they have received in other publications.

The function Hindex calculates the authors’ H-index or the sources’ H-index and its variants (g-index and m-index) in a bibliographic collection.
```{r}
authors <- gsub(","," ",names(results$Authors)[1:10])

indices <- Hindex(M, field = "author", elements=authors, sep = ";", years = 50)

indices$H
```

### Top-Authors’ Productivity over the Time
The function AuthorProdOverTime calculates and plots the authors’ production (in terms of number of publications, and total citations per year) over the time.
```{r}
topAU <- authorProdOverTime(M, k = 10, graph = TRUE)
head(topAU$dfAU)
```

## Bibliometix Network
```{r}
A <- cocMatrix(M, Field = "SO", sep = ";")
sort(Matrix::colSums(A), decreasing = TRUE)[1:5]
```
### Visualizing Bibliographics Networks
```{r}
# Create Country Collaboration Network
M <- metaTagExtraction(M, Field = "AU_CO", sep = ";")
NetMatrix <- biblioNetwork(M, analysis = "collaboration", network = "countries", sep = ";")

# Plot the network
#net <- networkPlot(NetMatrix, n = dim(NetMatrix)[1], Title = "Country Collaboration", type = #"circle", size=TRUE, remove.multiple=FALSE,labelsize=0.7,cluster="none")

# Create a co-citation network
 NetMatrix <- biblioNetwork(M, analysis = "co-citation", network = "references", sep = ";")
# Plot the network
net=networkPlot(NetMatrix, n = 30, Title = "Co-Citation Network", type = "fruchterman", size=T, remove.multiple=FALSE, labelsize=0.7,edgesize = 5)
```


